---
title: "Exploring ARGO data"
author: "Nicholas Baetge"
date: "3/4/2021"
output: github_document
---

This project pulls [synthetic](https://argo.ucsd.edu/data/data-faq/#RorD) ARGO data from the [web](http://www.argodatamgt.org/Access-to-data/Access-via-FTP-or-HTTPS-on-GDAC) using the argoFloats package, which is still developing but is super sweet. That package can be found [here](https://argocanada.github.io/argoFloats/index.html) Data are then extracted from nested lists into a dataframe to ease exploration via ggplot. 

# Libraries

```{r}
library(oce)
library(ocedata)
# library(devtools)
#    install_github('dankelley/argoFloats', ref='develop')
library(argoFloats)
library(ncdf4)
```

# Download and Index

```{r}
synthetic <- getIndex("synthetic", destdir = "~/GITHUB/argo/synthetic_data/")

from <- as.POSIXct("2020-03-01", tz = "UTC")
to <- as.POSIXct("2021-03-07", tz = "UTC")
subset.geo <- subset(synthetic, circle = list(longitude = -16.5, latitude = 49, radius = 222 )) 
subset.time <- subset(subset.geo, time = list(from = from, to = to))  

```

# Plot Float Locations

```{r}
plot(subset.geo, bathymetry = FALSE, mar = par("mar"),  asp = 1 / cos(mean(range(unlist(subset.geo[["latitude"]]), na.rm = TRUE))*pi/180),  mgp = getOption("oceMgp"))

```

# Download and QC Indexed Profiles

```{r}
profiles <- getProfiles(subset.geo, destdir = "~/GITHUB/argo/synthetic_data/")
argos <- readProfiles(profiles, destdir = "~/GITHUB/argo/synthetic_data/")
argosClean <- applyQC(argos) #fills flagged bad data with "NA"

 
```

# Plot T-S

```{r}
plot(argosClean, which = "TS")
```

# Extract Data from Nested Lists

```{r}
library(tidyverse)
library(lubridate)

list <- argosClean@data$argos

getdata <- function(i){x <- i@data }

getnames <- function(i){x <- i@metadata$filename
y <- gsub("/Users/nicholasbaetge/GITHUB/argo/synthetic_data/", "", x)
z <- gsub(".nc", "", y)}

data <- lapply(list, getdata)
names <- lapply(list, getnames )

names(data) <- names

convert <- function(i) {
   cols <- names(i)
   i$time <- as.character(i$time)
   b <- as.data.frame(do.call("cbind", i))
   colnames(b) <- cols
   c <- b %>% 
  mutate_at(vars(-time), as.numeric) %>% 
  mutate(date = ymd_hms(time),
         year = year(date),
         month = month(date)) %>% 
  select(date, year, month, everything(), -time)
  }

data.convert <- lapply(data, convert)

tidied <- plyr::ldply(data.convert, data.frame) %>% 
  separate(.id, into = c("float", "profile"), sep = "_") 

```

# Plot Profiles

```{r fig.height=6, fig.width=30, message=FALSE, warning=FALSE}

library(viridis)
library(ggpubr)

tidied %>% 
  filter(pressureAdjusted < 500) %>%
  ggplot(aes(x = pressureAdjusted, y = temperatureAdjusted, group = interaction(float, profile))) +
  facet_grid(~as.factor(month)) +
  geom_line(aes(color = as.factor(year)), size = 2, alpha = 0.3) +
  labs(x = "Pressure, dbar", y = "Temperature, ˚C", color = "Year") +
  # expand_limits(x = 200) +
  scale_x_reverse() +
  coord_flip() +
  scale_color_viridis_d() +
  # guides(colour = F, fill = F, shape = F, linetype = F) +
  theme_classic2(base_size = 20) +
  theme(legend.title = element_blank(),
        panel.spacing.x = unit(1, "cm"),
        axis.text.x = element_text(angle = 0),
        legend.key.size = unit(1, "cm"))

```




